Technical Report

### 2018-06-19 fully-abstract-comp/technical-report.tex
Clarify comment.
Made ce reasonable definition downwards closed.

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps
  if:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \item $0 < i \le n$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behaves reasonably up to
      $n-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and
      $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \item $0 < i \le n$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$
      and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$.
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \item $0 < i \le n$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $0 < i \le n$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n$ steps for
    all $r$ (including $\pcreg$)
  \end{itemize}  
\end{definition}

@@

>>>>

\begin{definition}[Reasonable configuration]
  \label{def:reasonable-conf}
  We say that an execution configuration $\Phi$ is reasonable up to $n$ steps
  iff for all $n' \le n$:
  \begin{itemize}
  \item \emph{Guarantee stack base address before call} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$
      for some $\src{r_1}$ and $\src{r_2}$
    \item $0 < i \le n'$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) =
      \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1 \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behaves reasonably up to
      $n'-i$ steps
    \end{itemize}
  \item \emph{Use return seals only for calls} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$
      and $\sigma \in \gsigrets$
    \item $\sigma \in \gsigcloss$.
    \end{itemize}
  \item \emph{Don't store private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps
  \item \emph{Don't leak private stuff...} If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \item $0 < i \le n'$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable in memory $\Phi'.\mem$ up to $n'-i$ steps for
    all $r$ (including $\pcreg$)
  \end{itemize}  
\end{definition}

@@

  \begin{lemma}
    \label{lem:ec-reasonable-downwards-closed}
    For all $n' \le n$ if
    \begin{itemize}
    \item $\Phi$ is reasonable up to $n$ steps
    \end{itemize}
    Then
    \begin{itemize}
    \item $\Phi$ is reasonable up to $n'$ steps
    \end{itemize}
  \end{lemma}
  \begin{proof}
    Follows by definition.
  \end{proof}
